---
title: "PSTAT131 Homework 4"
author: "Shivani Kharva"
date: "2022-10-31"
output:
  html_document:
    toc: true
---

### Initial Setup  

```{r, message = FALSE}
# Loading the data/ packages
pokemon_data <- read.csv("data/Pokemon.csv")
library(tidymodels)
library(ISLR)
library(tidyverse)
library(discrim)
library(poissonreg)
tidymodels_prefer()
```

### Exercise 1  
```{r}
# Loading in the `janitor` package
library(janitor)

# Using clean_names() on the pokemon data
pokemon_clean <- clean_names(pokemon_data)

# For comparison ...
head(pokemon_data)
head(pokemon_clean)
```

It appears that clean_names() changed the column names to a cleaner format without any extra characters or symbols and all in lower-case font. I think clean_names() is useful because it cleans up the variable names and simplifies them. If variable names are complicated, it can become confusing so having a function like clean_names() that automatically simplifies the variable/column names is quite useful.  

### Exercise 2  











